### 2016-10-18 methodsPaper/tex/materialsAndMethods.tex
CDC WONDER methods

>>>>

We report total change (averted or increased) in diability adjusted life years (DALYs) as an estimate of dissease burden change with alternative scenarions. To estimate DALYs we use a methodology adopted from previous US implementations of ITHIM  which scale Global Budern of Disease Estimates for the US to smaller populations using mortality rate ratios \cite{Maizlish2013}. Age, sex, and casuse specific mortalities were obtained form the CDC WONDER database for US metro counties for the years 2010-2014. Cells with less than 10 deaths were imputed using R's random integer generator.
